\documentclass[10pt]{report}

\author{......}
\title{Something, Yet Nothing.}
\usepackage{shapepar}
\usepackage{longtable}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
 
\begin{document}
\maketitle
\tableofcontents

\newpage
\section{About}

	This is a 5e Dungeons and Dragons Adventure which is recommended for 1st level adventurors. Have fun. \\
	
	Please note: Although for 1st levels initially, it is highly recommended to make up more interesting monsters on the spot. 

\part{\textit{Something, Yet Nothing.}}
\chapter{And So It Begins... Or Does It?}

    The party will begin in one of the following places at the DM's descretion.
    
\section{The Village of Yerne}
\begin{multicols}{2}
	Yerne is a small village of about 800 human villagers. This is a rather peaceful village situated somewhere near the human/dwarf border. There are a few forges, shops, inns, and markets in this village, but not much about magic is here.
	
\subsection{The Town Hall}The town hall is a moderately furnished wooden building with about 1500 square feet. Owlbear heads are hung on the wall, with a few display weapons here and there. The mayor, Edgar can be found here. Edgar is a fairnatured 5'9" man that wields a short sword, but it can easily be seen that he isn't meant for fighting. \\



	
	
\columnbreak
The Mayor, Edgar\\
Lv. 3 Lawful Good \\
HP: 2D8 + 14 (19) AC: 10 \\
Str: 13 (+1) Dex:  8 (-1) \\
Con: 14 (+2) Int: 15 (+2) \\
Wis: 15 (+2) Cha: 13 (+1) \\
Move: 30ft Initiative: +1 \\
Attacks: 
\medskip \\
Short Sword (1D6 + 1)  \\
Slash, + 3 to Hit 
\medskip \\
Drops: 40 gp, \textit{Short Sword} \\
Experience: 70 EXP \\


\end{multicols}

He seems to know a lot about the village though, and can be persuaded to reveal a secret passage inside the village that allows villagers to traverse to any building undetected from invaders via trapdoors in all of their basements - except for a particular inn that refuses to join the network after the murder of the orginal innkeep. 


\paragraph{Availible Jobs And Quests :} If asked for work, Edgar will ask the adventurers to help hunt meat for an annual festival tomorrow. The town will pay 4 sp per kilogram of meat, but they want at least 40 kilograms. After completing this mission, the mayor will ask if they want to stay overnight to join the festivities. If they do accept, he will direct you to the mysterious innkeep with a note that will allow the adventurers to stay one night at the innkeep for free. 

\paragraph{The Festival :} When the festival occurs, there will be free small meals and mead, but the adventurers will notice that not a lot of people are there. If the adventurers know about the hidden passage network, they can enter the network to enjoy the full festivities, where adventurers will also find dance desplays and (somehow) fireworks.

\subsection{The Mysterious Innkeep}
Going to the innkeep that the mayor mentions will land the adventurors to enter a door. This door opens easily, with just a little force. Upon entry, a 16 year old girl welcomes you, and introduces herself as Helen. \\

\begin{multicols}{2}
Helen is a 4'9" human that, if perceived (Perception 22) has a tome to cast fireball at intruders. She seems a bit sad, but will offer you a rather comfortable room for 2 sp. The inn itself contains warm wood furnishings and family portraits. If the adventurors ask about the portraits, Helen will start to tear a little after she talks about her family - her father was executed for a murder they later found he did not commit, the victim being her mother. 

The room offered has comfortable beds, enchanted lamps, and a sturdy desk. Sleeping in the bed has a chance (NAT 15) of the adventurer becoming \textit{well rested}, which grants a double XP yield on their furst encounter. \\

\columnbreak
The Orphan Inkeep, Helen \\
Lv. 4 True Neutral \\
HP: 3D6 + 2 (11) AC: 16 \\
Str: 8 (-1) Dex:  16 (+3) \\
Con: 9 (-1) Int: 18 (+4) \\
Wis: 15 (+2) Cha: 16 (+3) \\
Move: 30ft Initiative: +3 \\
Attacks: 
\medskip \\
\textit{Fireball} (1D10)  \\
Fire, + 6 to Hit 
\medskip \\
\textit{Damuscus Knife} (1D4 + 3) \\
Slash, Throw, +3 to Hit, \\
Enemy AC -2 for 2 turns. 
\medskip \\
Drops: 60 gp, 
\medskip \\
 \textit{Damuscus Knife}  \\
(+1 Dmg, -2 Enemy AC over 2 turns) 
\medskip \\
Experience: 110 EXP \\

\end{multicols}

If an adventuror examines the lamp, they might roll an Arcana roll (DC18) to aquire the spell \textit{Burning Hands}. If they fail this roll, however, they burn themself, taking 1D4 fire damage. If the desk is examined, adventurers will find that it is reinforced with carbon, and although it \textit{can} be used to create a rather sturdy (grants +1 Hit) weapon, you will need to pay 300 gp for the damages.

\subsection{The Merchants' Mart}

The \textit{Merchants' Mart} is a rather large building of about 12000 square feet with 2 floors. When the adventurors walk inside, they will find that the buildings are split into 5 major compartments.

\paragraph{The Forge:}

To the far right of the door the adventurers walk through is the forge department. Inside, you will find many blacksmiths forging weaponry and armor, and a couple of clerks. The store will sell all basic weapons and \textit{most} martial weapons in iron. They also, however, carry tamahagane katanas and knives, damuscus sabres, knives, and swords, adamentine swords, and a wide selection of basic armor.
\textit{Note: Tamahagane weapons cost 435 gp more than the iron variants, damuscus weapons cost 280 gp more, and adamentine cost 3000 gp more.}

\paragraph{The General Store:}

A bit to the right of the entrance the adventurers can find the general store. They will be able to find most normal goods here, including food and dungeoneering supplies.

\paragraph{The Bar:}

\begin{multicols}{2}
When the adventurers walk into the bar, they will find it as a cozy area with quant wooden tables. The barkeep, Orcus, is usually silent, but if you ask him for a bottle of beer, he will speak. He charges 3 cp for beer, but 6 sp for good quality wine.

In the bar there are also dancers if the adventurers come after 10 PM. They are usually quite talkative and flirty, but be careful - Orcus is very protective for his employees.\\

\columnbreak
The Barkeep, Orcus \\
Lv. 4 True Neutral \\
HP: 3D8 + 20 (33) AC: 12 \\
Str: 15 (+2) Dex: 12 (+1) \\
Con: 19 (+4) Int:  9 (-1) \\
Wis: 8  (+2) Cha: 11 ($\pm$ 0) \\
Move: 30ft Initiative: $\pm$ 0 \\
Attacks: 
\medskip \\
\textit{Beer Bottle} (1D4 + 2)  \\
Blugeoning Damage, + 4 to Hit 
\medskip \\
Drops: 35 gp. 
\medskip \\
Experience: 110 EXP \\
\end{multicols}

\paragraph{The Arcane Shop}
In here, adventurers will find a rustic wooden store with neatly shelfed bookcases. There are a lot of tomes on basic magic use (Up to Lv. 3) here, but they are not cheap. They may also stock \textit{some} enchanted tools, but the selection should be minimal at best.

\paragraph{The Apothricary}
In the far left lies the apothricary, where potions can be sold. The potions and reagants here should be ample, but not great in terms of selection. The adventurers will notice that 

\part{Extra Monsters, Weapons, and Other Lore}
  
\section{New Materials}
	You can probably make new weapon materials on the spot. Who knows, maybe you will decide it would be cool to make a \textit{LED} dagger or something that lights up when powered. But in any case, I took the liberty to look up and create a few of my own.ff
	
	\begin{longtable}[c]{| c | c |}
 
 \hline
 \multicolumn{2}{| c |}{Weapon Materials}\\
 \hline
 Name & Effect\\
 \hline
 \endfirsthead
 

\hline
 \endlastfoot
 
 Tamahagane & Rare. Increases threat range by 2, critical multiplier by 2.\\
 Damuscus & Increases real damage by 1, enemy loses 1 AC for 2 turns.\\
 Lead & Extremely heavy. Requires 13+ strength. Toxic, but grants +3 true damage.\\
 Teflon & Not really suited for weapons. -1 true damage. Non-stick.\\
 Wood & Good for practice weapons. -2 true damage, +2 hit. Can not critical. \\
 Gold & -3 true damage. Expensive. Not really a good material to make weapons. Shiny. \\
 Dragontooth & +1 true damage. +1 Hit. If this successfully hits a dragon, it's critical. \\
 Concrete & +1 true damage. -4 Hit. Heavy and unsuitable for combat. \\
 Friendship & +5 Hit, +3 True Damage, +5 AC. Only can be used when things look grim.\\
 Dark Steel & +1 Hit against Good Enemies. You feel the corruption in your blood. Evil only. \\
 
 \end{longtable}

\end{document}


